### 2014-12-02 doc/GMP2015/sample/sample.tex
Added documents.

%
% put the title of your paper here
%
\title{Optimal Decomposition-Recombination Plans for 2D Well-Constrained Graphs}

%
% put your submission number here
% this number will appear instead of authors and affiliations if the class option "submission" is active
%
\SubNumber{X}

%
% put the author names here
% use the second argument as a reference to the list of affiliations
% no authors and affiliations will appear if the class option "submission" is active
%
\author{Troy Baker}{1}
\author{Meera Sitharam}{1}
\author{Menghan Wang}{1}

%
% put the affiliations of the authors here
%
\affiliation{1}{Department of Computer and Information Science and Engineering, University of Florida, USA}

@@

\begin{abstract}
Super awesome abstract.
\end{abstract}

@@

\begin{figure}\centering
  \includegraphics[scale=.5]{example.eps}
  \caption{Example of a normal figure that spans one column.}
  \label{fig:square}
\end{figure}

@@

\begin{figure*}\centering
\includegraphics{example.eps}
\caption{Example of a figure that spans both columns.}
\end{figure*}

@@

\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

%
% put the title of your paper here
%
\title{A nice paper that is being submitted to GMP 2015}

%
% put your submission number here
% this number will appear instead of authors and affiliations if the class option "submission" is active
%
\SubNumber{142}

%
% put the author names here
% use the second argument as a reference to the list of affiliations
% no authors and affiliations will appear if the class option "submission" is active
%
\author{Alvin B.\ Ginner}{1}
\author{Douglas Smith}{1}
\author{Martha X.\ Pert}{2}

%
% put the affiliations of the authors here
%
\affiliation{1}{Department of Computer Science, University of Smalltown, Germany}
\affiliation{2}{Department of Mathematics, University of Excellence, USA}

@@

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse eleifend diam augue. Donec adipiscing mollis nisl vitae porttitor. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas gravida tincidunt volutpat. Morbi sapien ligula, commodo quis dignissim non, aliquam nec urna. Vivamus quis massa sit amet mi convallis sagittis ac facilisis velit. Duis at eros purus, vel laoreet nibh. Suspendisse rutrum est vel massa imperdiet at ultricies massa facilisis. Sed vitae pulvinar magna.
\end{abstract}

@@

\begin{figure}\centering
  \includegraphics[scale=.5]{example}
  \caption{Example of a normal figure that spans one column.}
  \label{fig:square}
\end{figure}

@@

\begin{figure*}\centering
\includegraphics{example}
\caption{Example of a figure that spans both columns.}
\end{figure*}

@@

\bibliographystyle{abbrv}
\bibliography{sample}

### 2014-12-02 doc/General_Work/notes-old.tex
Added documents.

\section{Definitions}
ISSUE: My definitions don't prevent non-positive densities... This means things aren't guaranteed to be connected...

\begin{definition}[Graph]
Graph $G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$. Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$.
\end{definition}

\begin{definition}[Density]
The density of a graph is defined as:
\[d(G) = \sum_{v\in V}{w_V(v)} - \sum_{e\in E}{w_E(e)}\]
% \[d(G) = \max\set{0,\sum_{v\in V}{w_V(v)} - \sum_{e\in E}{w_E(e)}}\]
\end{definition}

\begin{definition}[Underconstrained Graph]
Graph $G=(V,E,w_V,w_E)$ is underconstrained if, given constant $k$, $d(G) > k$.
\end{definition}

\begin{definition}[Overconstrained Graph]
Graph $G=(V,E,w_V,w_E)$ is overconstrained if, given constant $k$, $d(G) < k$.
\end{definition}

\begin{definition}[Wellconstrained Graph]
Graph $G=(V,E,w_V,w_E)$ is wellconstrained if, given constant $k$ and a set of trivial graphs $T$, the graph satisfies (1) $d(G)=k$ and (2) all subgraphs are either underconstrained, wellconstrained, or trivial (i.e.\ are isomorphic to one of the graphs in $T$).
\end{definition}

@@

\section{Notation}
$G$ is taken to be a graph with values $(V,E,w_V,w_E)$. To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies if there are no constraints between them. Furthermore, to limit the scope of the paper, $G$ will always be taken to be wellconstrained. THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.

@@

$C$ is an arbitrary graph in a node in $DRP(G)$. $C_i$ is the $i^{\text{th}}$ child of $C$. By definition of a DR-plan, it is implied that $C_i$ is a wellconstrained vertex-maximal proper subgraph.

@@

    \node[v] (v1) at (1,1) {$C'_j$};
    \node[v] (v2) at (3,1) {$C'_k$};
    \node[v] (v3) at (2,2) {$D$};
    \node[v] (v4) at (2,3.3) {$C'_i$};

    \tedge{v1}{v3}{solid}{}{above};
    \tedge{v2}{v3}{solid}{}{above};
    \tedge{v3}{v4}{solid}{}{right};
\end{tikzpicture}
\ldots with weights \ldots
\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

@@

We develop this notion of the canonical optimal DR-plan by carefully considering the case of a union of any two nontrivial wellconstrained vertex-maximal proper subgraphs of a wellconstrained graph. By definition, any subgraph of a wellconstrained graph will either be (1) trivial, (2) underconstrained, or (3) wellconstrained. We will analyze all 3 possibilities in turn. These observations will lead to interesting properties that govern the behavior of optimal DR-plans on wellconstrained graphs.

@@

\subsection{Lemmas for Union and Intersection Relationships}
\begin{lemma}\label{t-l1}
Given two wellconstrained subgraphs $F_i,F_j$, $F_i\cup F_j$ cannot be trivial.
\end{lemma}

\begin{proof}
% If $F_i,F_j$ are wellconstrained, then $F_i\cup F_j \geq k$. Trivial graphs must be overconstrained.

@@

\begin{lemma}\label{uc-l1}
Given two wellconstrained subgraphs $F_i,F_j$, $F_i\cup F_j$ is underconstrained if and only if $F_i\cap F_j$ is trivial.
\end{lemma}

\begin{proof}
This can be shown with simple arithmetic. It follows from definitions that $d(F_i)=k$ and $d(F_j)=k$. In the forward direction we have that $d(F_i\cup F_j)=l>k$, therefore $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)=2k-l<k$. The only way to have an overconstrained subgraph in a wellconstrained graph is if it is trivial. In the backwards direction the same math proves it.
\end{proof}

\begin{lemma}\label{wc-l1}
Given two wellconstrained subgraphs $F_i,F_j$, $F_i\cup F_j$ is wellconstrained if and only if $F_i\cap F_j$ is wellconstrained.
\end{lemma}

\begin{proof}
This can be shown with simple arithmetic. It follows from definitions that $d(F_i)=k$ and $d(F_j)=k$. In the forward direction we have that $d(F_i\cup F_j)=k$, therefore $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)=k$. Thus $F_i\cap F_j$ is wellconstrained. In the backwards direction the same math proves it.

Furthermore, all subgraphs of $F_i\cup F_j$ and $F_i\cap F_j$ are also subgraphs of $F_i$ and $F_j$, therefore all properties of wellconstrained graphs are maintained.

% In the forward direction: From Lemma \ref{uc-l1}, the intersection cannot be trivial. The intersection also cannot be underconstrained. If $F_i \cap F_j$ were underconstrained, then for $F_i$ to be wellconstrained you would need to add more constraints (edge weight) than degrees of freedom (vertex weight) to the intersection. The same is true for $F_j$. If both of these were satisfied, then the union of $F_i$ and $F_j$ would result in an overconstrained nontrivial graph. This is a contradiction, by definition of a wellconstrained graph. Therefore, the intersection can only be wellconstrained.

% BACKWARDS!!!!!
\end{proof}

\begin{lemma}\label{iuc-l1}
Given two wellconstrained subgraphs $F_i,F_j$, $F_i\cap F_j$ cannot be underconstrained.
\end{lemma}

\begin{proof}
Subgraphs of wellconstrained graph $G$ can only be trivial, underconstrained, or wellconstrained. So it follows from Lemmas \ref{t-l1}, \ref{uc-l1}, and \ref{wc-l1} that only trivial and wellconstrained intersections are possible.
\end{proof}

\subsection{Lemmas for Intersection and Graph Structure Relationships}

\begin{lemma}\label{wc-l2}
% Given a wellconstrained $G$ and two wellconstrained vertex-maximal proper subgraphs $C_i, C_j$,
$C_i\cup C_j$ is wellconstrained if and only if $C_i\cup C_j = C$.
\end{lemma}

The backwards direction follows from the fact that $C$ is either some non-leaf node (wellconstrained by definition of a DR-plan) or $G$ itself (wellconstrained by definition of the problem).
\end{proof}

\begin{corollary}\label{wc-c1}
% Given a wellconstrained $G$ and two wellconstrained vertex-maximal proper subgraphs $C_i, C_j$, l
Let us say $R_i=C\setminus C_i$ and $R_j=C\setminus C_j$. If $C_i\cup C_j$ is wellconstrained, then there can be no edges in $G$ between the vertices of $R_i$ and $R_j$.
\end{corollary}

\begin{proof}
It follows from the fact that $C_i\cup C_j$ must equal $C$ (proven in Lemma \ref{wc-l2}).
\end{proof}

% \begin{corollary}
% Given the same conditions: $R_i$ and $R_j$ must be connected to $D_{i,j}=C_i\cap C_j=C\setminus R_i\setminus R_j$.
% \end{corollary}

% \begin{proof}
% From Lemma \ref{wc-l1}, $D_{i,j}$ must be wellconstrained.
% \end{proof}

\begin{lemma}
asdfas
\end{lemma}

\begin{proof}
Let us say $R_i=C\setminus C_i$, $R_j=C\setminus C_j$, and $D_{i,j}=C_i\cap C_j=C\setminus R_i\setminus R_j$ (note that $R_j\subset C_i$, $R_i\subset C_j$ and $D_{i,j}\subset C_i,C_j$). Furthermore, $R'_i\subset R_i$, $R'_j\subset R_j$, and $D'_{i,j}\subset D_{i,j}$ which are not empty sets.

Then we assume that there is some third wellconstrained vertex-maximal proper subgraph $C_k$ (with $C'_k=C\setminus C_k$). There are $3\times 3\times 3 = 27$ possible cases for what this subgraph could be.

% \begin{enumerate}
%     \item Assume $C_k\cup C_i \neq C$ and $C_k\cup C_j \neq C$. Then from Lemma \ref{wc-l2} $C_k\cup C_i$ is not wellconstrained and must therefore be underconstrained. Furthermore, $C_k\cup C_i=Idc(C,R'_i\cup C_i)$ because $C_k\neq C_i$. This means the subgraph $R'_i$ and its edges between $C_i$ increase the density overall because $C_i$ is wellconstrained. Similarly, the same is true for $R'_j$ and its edges. Since there can be no edges between $R'_i$ and $R'_j$ (COROLLARY, wouldn't be $C$!!!!) it means that all of the edges connecting them are incident to $D_{i,j}$. Therefore, $Idc(C,R'_i\cup R'_j\cup D_{i,j})$ should be underconstrained. However, by Lemma \ref{uc-l1}, using the two underconstrained graphs we have that $(C_k\cup C_i)\cap (C_k\cup C_j)=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ so it must be trivial which is a contradiction, so $C_k$ could not be a wellconstrained vertex-maximal proper subgraph.
%     % Similarly, we find the $C_k\cup C_j=Idc(C,R'_j\cup C_j)$ is underconstrained. However, $(C_k\cup C_i)\cap (C_k\cup C_j)=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ which is wellconstrained. This contradicts Lemma \ref{wc-l1} so $C_k$ could not be wellconstrained.
%     \item Assume $C_k\cup C_i\neq C$ and $C_k\cup C_j= C$. Similar to the first case, we see that

%     If it's just one and the other does equal C, then the other is not vertex-maximal?
%     \item If it's neither... well then you either have C or the solution.
% \end{enumerate}

\begin{itemize}
    \item 3 cases: $C_k$ cannot be $C=Idc(C,R_i\cup R_j\cup D_{i,j})$, $C_i=Idc(C,R_j\cup D_{i,j})$, or $C_j=Idc(C,R_i\cup D_{i,j})$. This is by definition.
    \item 13 cases: $C_k$ cannot be a proper subgraph of $C_i$ and $C_j$ or else $C_k$ would not be vertex-maximal. These are the graphs $Idc(C,R'_i\cup D_{i,j})$, $Idc(C,R'_j\cup D_{i,j})$, $Idc(C, D_{i,j})$, $Idc(C,R_i\cup D'_{i,j})$, $Idc(C,R_j\cup D'_{i,j})$, $Idc(C,R'_i\cup D'_{i,j})$, $Idc(C,R'_j\cup D'_{i,j})$, $Idc(C, D'_{i,j})$, $Idc(C,R_i)$, $Idc(C,R_j)$, $Idc(C,R'_i)$, $Idc(C,R'_j)$, and $Idc(C,\emptyset)$.
    \item 2 cases: $C_k$ cannot contain $C_i$ or $C_j$ as proper subgraphs, or else they were not vertex-maximal. These are the graphs $Idc(C,R'_i\cup R_j\cup D_{i,j})$ and $Idc(C,R_i\cup R'_j\cup D_{i,j})$ respectively.
    \item 4 cases: $C_k$ cannot be $Idc(C,R_i\cup R_j)$, $Idc(C,R'_i\cup R_j)$, $Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$...
    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since $C_k\cup C_i = Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{wc-l2} that $C_k\cup C_i$ cannot be wellconstrained. We also know it cannot be trivial because it contains wellconstrained subgraphs. This means it must be underconstrained. From Lemma \ref{uc-l1}, we know that $C_k\cap C_i=Idc(C,R'_j\cup D_{i,j})$ must then be trivial. This is impossible because $D_{i,j}$ is wellconstrained, thereby contradicting the assumption that $C_k$ is wellconstrained.
    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D'_{i,j})$ is not possible...
    %
    \item 2 cases: $C_k=Idc(C,R'_i\cup R_j\cup D'_{i,j})$ and $C_k=Idc(C,R_i\cup R'_j\cup D'_{i,j})$ are not possible...
    %
    \item 1 case: $C_k=Idc(C,R_i\cup R_j\cup D'_{i,j})$ is all that is left!
\end{itemize}

The weight of $R_i$ has to be exactly equal to the weight of the edges that connect it to $D_{i,j}$. It must add 0 weight exactly since $D_{i,j}$ is wellconstrained.

There can't be an intersection that is underconstrained between to wellconstrained graphs!

\begin{itemize}
    \item $C_k$ cannot be $Idc(C,R_i\cup R_j)$. From Corollary \ref{wc-c1}, $R_i$ and $R_j$ must not have any edges between them. Without loss of generality, we can say that $d(R_i)=l$ and $d(R_j)=k-l$. Because $C_i$ and $C_j$ are wellconstrained, and so is $D_{i,j}$, $R_i$ with its edges must add 0 density and $R_j$ with its edges must add 0 density. Since edges must have positive weight, $l\geq 0$ and $k-l\geq 0$ so $d(R_i)\in [0,k]$ and $d(R_j)\in [0,k]$ with $d(R_i)+d(R_j)=k$. This means, without loss of generality, that at least $R_i$ is trivial
    %
    % \item 1 case: $C_k=Idc(C,R_i\cup R_j)$ is not possible...
    % \item 1 case: $C_k=Idc(C,R'_i\cup R'_j)$ is not possible...
    % \item 2 cases: $C_k=Idc(C,R'_i\cup R_j)$ and $C_k=Idc(C,R_i\cup R'_j)$ are not possible...
    % \item 4 cases: $C_k$ must contain a subgraph of $D_{i,j}$. Consider if it did not, then $C_k\cap D_{i,j}=\emptyset$ which is necessarily a trivial graph. By Lemma \ref{uc-l1}, this implies that $C_k\cup D_{i,j}$ is underconstrained, so $d(C_k\cup D_{i,j})>k$. Because there is no intersection, $d(C_k\cup D_{i,j})=d(C_k)+d(D_{i,j})$. However, we know that $D_{i,j}$ is wellconstrained, so $d(D_{i,j})=k$. This means that $d(C_k)$ must be greater than $k$ which makes it underconstrained, contradicting the assumption. This means $C_k$ cannot be $C_k=Idc(C,R_i\cup R_j)$, $C_k=Idc(C,R'_i\cup R_j)$, $C_k=Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$.
    %
    \item 4 cases: $C_k$ must contain a subgraph of $D_{i,j}$. Take $C_k=Idc(C,R_i\cup R_j)$. In this case, $C_k\cup C_i = R_i\cup C_i$ which does not equal $C$ because it is missing the edges between $R_i$ and $D_{i,j}$. We have from Lemma \ref{wc-l2} that this union cannot be wellconstrained. It cannot be trivial because it has wellconstrained subgraphs which leaves it to be underconstrained. We know $C_i$ is wellconstrained, therefore it must be $R_i$ that is underconstrained. This can be used to show that $R_j$ is also underconstrained. This means $R_i\cup R_j=C_k$ must be underconstrained, contradicting the assumption. This proof holds for several other cases, meaning $C_k$ cannot be $Idc(C,R_i\cup R_j)$, $Idc(C,R'_i\cup R_j)$, $Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$.
    %
    %
    %
    % \item $Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. If this were wellconstrained the intersection with $C_i$ would be wellconstrained, which is $Idc(C,R'_j\cup D_{i,j})$. Similarly, it would imply
    \item $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since this graph's union with $C_i$ is $Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{wc-l2} that this union cannot be wellconstrained (and must therefore be underconstrained). We know $Idc(C,R_j\cup D_{i,j})=C_i$ is wellconstrained which implies $R'_j$ and the edges incident to it are increasing the density. Using the same process, we can show the same for $R'_i$. Since $D_{i,j}$ is wellconstrained, adding two components that increase the density would mean that $Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is underconstrained, contradicting the assumption.
    %
    \item $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ and $C_k=Idc(C,R'_i\cup R'_j\cup D'_{i,j})$ are not possible. In both scenarios we have $C_k\cup C_i \neq C$ and $C_k\cup C_j \neq C$. From Lemma \ref{wc-l2} $C_k\cup C_i$ cannot be wellconstrained and must therefore be underconstrained. Furthermore, $C_k\cup C_i=Idc(C,R'_i\cup C_i)$ because $C_k\neq C_i$. This means the subgraph $R'_i$ and its edges between $C_i$ increase the density overall because $C_i$ is wellconstrained. Similarly, the same is true for $R'_j$ and its edges. Since there can be no edges between $R'_i$ and $R'_j$ (COROLLARY, wouldn't be $C$!!!!) it means that all of the edges connecting them are incident to $D_{i,j}$. Therefore, $Idc(C,R'_i\cup R'_j\cup D_{i,j})$ should be underconstrained. However, by Lemma \ref{uc-l1}, using the two underconstrained graphs we have that $(C_k\cup C_i)\cap (C_k\cup C_j)=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ so it must be trivial which is a contradiction, so $C_k$ could not be a wellconstrained vertex-maximal proper subgraph.
    % \item $C_k=Idc(C,R'_i\cup R'_j\cup D'_{i,j})$ is not possible...
\end{itemize}
\end{proof}

\pagebreak
See ISSUE at top of paper, we have to assume we have a connected $G$...

Take $C'_i$ to be $C\setminus C_i$. Then if $C_i\cup C_j$ is wellconstrained we have directly from Lemma \ref{wc-l2} for all $C'_i, C'_j$ there can be no edges between them (otherwise $C_i\cup C_j\neq C$).

The set of edges connecting $C'_i$ to $C_i$ must have a weight that sums to exactly $d(C'_i)$ since we know that $d(C)=d(C_i)=k$.

Any other $C_k$ must therefore contain $C'_i$ and $C'_j$ because it adds no density to ``tack it on'' to a graph that does not contain them already.

Now we want to know something about $C_k$. If $C_k \neq C_i$, then $C'_i\not\subseteq C'_k$. It is clear that they cannot be equal otherwise $C_k = C_i$. However, it also cannot be a subset. There are two scenarios. (1) $C'_k$ does not contain vertices that are incident to $C'_i$. If this were so, we know we could ``tack on'' $C'_i$ to the wellconstrained $C_k$ without increasing the density and therefore $C_k$ could not have been maximal in the first place. (2) $C'_k$ contains vertices that are incident to $C'_i$. In this case

Take $D_{i,j}$ to be $C\setminus (C'_i\cup C'_j)$. Clearly $D_{i,j}$ must be wellconstrained since ``tacking on'' $C'_i$ and $C'_j$ adds no density and $C$ is wellconstrained. Therefore, if there were some other $C_k$, it must contain $D_{i,j,k}\subset D_{i,j}$ such that $D_{i,j,k}=D_{i,j}\setminus C'_k$. It is clear that $D_{i,j,k}$ cannot equal $D_{i,j}$ or else $C_k$ must be $C_i$ or $C_j$ to be vertex-maximal.

@@

\begin{proof}
By Lemmas... the union must be under
Lemma \ref{uc-l1} that $C_i\cup C_j$ must be underconstrained. Therefore, by the proof
It follows from Lemma \ref{wc-l1} that the only way to get
 and its proof that if any intersections
\end{proof}

\subsection{Theorems for Optimal DR-Plans}

\subsection{Union is Underconstrained}

@@

>>>>

\section{Definitions}
\begin{definition}[Graph]
Graph $G=(V,E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$. Additionally, there are two weight functions, $w_V: V \to \mathbb{R}$ and $w_E: E \to \mathbb{R}$.
\end{definition}

\begin{definition}[Density]
The density of a graph is defined as:
\[d(G) = \sum_{v\in V}{w_V(v)} - \sum_{e\in E}{w_E(e)}\]
\end{definition}

\begin{definition}[Underconstrained Graph]
Graph $G=(V,E)$ is underconstrained if, given constant $k$, $d(G) > k$.
\end{definition}

\begin{definition}[Overconstrained Graph]
Graph $G=(V,E)$ is overconstrained if, given constant $k$, $d(G) < k$.
\end{definition}

\begin{definition}[Wellconstrained Graph]
Graph $G=(V,E)$ is wellconstrained if, given constant $k$ and a set of trivial graphs $T$, the graph satisfies (1) $d(G)=k$ and (2) all subgraphs are either underconstrained, wellconstrained, or trivial (i.e.\ are isomorphic to one of the graphs in $T$).
\end{definition}

@@

\section{Notation}
$G$ is taken to be a graph with vertex set $V$ and edge set $E$.

@@

$C$ is an arbitrary graph in a node in $DRP(G)$. $C_i$ is the $i^{\text{th}}$ child of $C$ (implied to be a wellconstrained vertex-maximal proper subgraph, by definition of a DR-plan).

@@

@@

We develop this notion of the canonical optimal DR-plan by carefully considering the case of a union of any two nontrivial wellconstrained vertex-maximal proper subgraphs of a wellconstrained graph. By definition, any subgraph of a wellconstrained graph will either be (1) trivial, (2) underconstrained, or (3) wellconstrained. We will analyze all 3 possibilities in turn.

@@

\subsection{Union is Trivial}
\begin{lemma}
The union of wellconstrained graphs cannot result in a trivial graph.
\end{lemma}

\begin{proof}
% If $C_i,C_j$ are wellconstrained, then $C_i\cup C_j \geq k$. Trivial graphs must be overconstrained.

@@

\subsection{Union is Underconstrained}
\begin{lemma}\label{uc-l1}
Given two wellconstrained subgraphs $C_i,C_j$, $C_i\cup C_j$ is underconstrained if and only if $C_i\cap C_j$ is trivial.
\end{lemma}

\begin{proof}
This can be shown with simple arithmetic. It follows from definitions that $d(C_i)=k$ and $d(C_j)=k$. In the forward direction we have that $d(C_i\cup C_j)=l>k$, therefore $d(C_i\cap C_j)=d(C_i)+d(C_j)-d(C_i\cup C_j)=2k-l<k$. The only way to have an overconstrained subgraph in a wellconstrained graph is if it is trivial. In the backwards direction the same math proves it.
\end{proof}

@@

\begin{proof}
Suppose
\end{proof}

@@

\begin{lemma}
Given two wellconstrained subgraphs $C_i,C_j$, $C_i\cup C_j$ is wellconstrained if and only if $C_i\cap C_j$ is wellconstrained.
\end{lemma}

\begin{proof}
In the forward direction: From Lemma \ref{uc-l1}, the intersection cannot be trivial. The intersection also cannot be underconstrained. If $C_i \cap C_j$ were underconstrained, then for $C_i$ to be wellconstrained you would need to add more constraints (edge weight) than degrees of freedom (vertex weight) to the intersection. The same is true for $C_j$. If both of these were satisfied, then the union of $C_i$ and $C_j$ would result in an overconstrained nontrivial graph. This is a contradiction, by definition of a wellconstrained graph. Therefore, the intersection can only be wellconstrained.

BACKWARDS!!!!!
\end{proof}

\begin{lemma}\label{wc-l2}
Given two wellconstrained vertex-maximal proper subgraphs $C_i, C_j$, $C_i\cup C_j$ is wellconstrained if and only if $C_i\cup C_j = C$.
\end{lemma}

The backwards direction follows from the definition of a DR-plan.
\end{proof}
